Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-05-29 neurips-20/cvx-flats.tex
tweaks

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{ccdim}}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}
\newcommand{\propdis}{\mu}
\newcommand{\affhull}{\mathrm{affhull}}

@@

\newcommand{\risk}[1]{#1^*}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\toto}{\rightrightarrows}
\neccommand{\ones}{\mathbbm{1}}

@@

For another application of Theorem~\ref{thm:bayes-risk-lower-bound}, consider any strictly concave function $G:\simplex\to\reals$ of the distribution.
It is well-known that $G$ is the Bayes risk of a proper loss defined by the Bregman divergence $L(p,y) = G(\delta_y) -G(p) - dG_p \cdot (\delta_y - p)$ where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$~\cite{gneiting2007strictly}\raf{other refs}.
For technical reasons, we need to modify $L$ so that the report space is $\reals^{n-1}$ by dropping a dimension, so that $L'(p',y) = L((p',1-\sum_{i=1}^{n-1}),y)$.
\raf{Gah I forgot how tricky this was...}

>>>>

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{ccdim}}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}
\newcommand{\propdis}{\mu}
\newcommand{\affhull}{\mathrm{affhull}}
\newcommand{\rank}{\mathrm{rank}}

@@

\newcommand{\risk}[1]{#1^*}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\ones}{\mathbbm{1}}

@@

For another application of Theorem~\ref{thm:bayes-risk-lower-bound}, consider any strictly concave function $G:\simplex\to\reals$ of the distribution.
It is well-known that $G$ is the Bayes risk of a proper loss defined by $L(p,y) = G(p) + s_p \cdot (\delta_y - p)$, where $\delta_y(y') = \ones\{y=y'\}$ is the point distribution on $y$ and $-s_p \in \partial (-G)(p)$ is a subgradient of $-G$ at $p$~\cite{gneiting2007strictly}\raf{other refs}.
For technical reasons, we need to modify $L$ so that the report space is $\reals^{n-1}$ by dropping a dimension, so that $L'(p',y) = L((p',1-\sum_{i=1}^{n-1}),y)$.
\raf{Gah I forgot how tricky this was...}
